%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\input{glyphtounicode}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape HARIHARAN E} \\ \vspace{1pt}
    Bengaluru, Karnataka, India \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ +91 8748937943 ~ \href{mailto:hariharanep@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{hariharanep@gmail.com}} ~
    \href{https://linkedin.com/in/hariharanep4/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/hariharanep4}}  ~
    \href{https://github.com/shreenivasa4/}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/shreenivasa4}}
    \vspace{-8pt}
\end{center}

%-----------SUMMARY-----------
% \section{Summary}
% \small{Experienced DevOps Engineer with 5 years of experience in managing infrastructure, automating deployments, and improving development pipelines. Proficient in cloud services, containerization, continuous integration/continuous deployment (CI/CD), and monitoring tools.}
% \vspace{-8pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming/Scripting Languages}{: Bash, Python, Go, Groovy} \\
     \textbf{CI/CD}{: Jenkins, GitHub Actions, Harbor, JFrog Artifactory, Argo CD, Flux CD} \\
     \textbf{Containerization \& Orchestration}{: Docker, Kubernetes, Helm} \\
     \textbf{Cloud Platforms}{: Amazon Web Services (EC2, VPC, S3, RDS, IAM, Route53, CloudWatch, EKS, Lambda)} \\
     \textbf{Infrastructure as Code}{: Terraform} \\
     \textbf{DevSecOps}{: SonarQube, Coverity, Trivy, Anchore, Black Duck, Kyverno, Kube-Bench} \\
     \textbf{Monitoring, Logging \& Tracing}{: Prometheus, Grafana, ELK Stack/OpenSearch, VictoriaMetrics, OTel, Jaeger} \\
     \textbf{Databases}{: PostgreSQL, Cassandra} \\
     \textbf{Networking and Security}{: OSI, TCP/IP, DNS, IPv4, HTTP/HTTPS, SSL/TLS, PKI} \\
     \textbf{GenAI Tools}{: OpenAI ChatGPT, Anthropic Claude, Google Gemini, GitHub Copilot}
    }}
 \end{itemize}
 \vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

   \resumeSubheading
      {Juniper Networks, Now Part of Hewlett Packard Enterprise (HPE)}{Aug 2025 -- Present}
      {Software Engineer 3 - DevOps}{Bengaluru, Karnataka}
      \resumeItemListStart
        % \resumeItem{Designed and implemented an end-to-end observability platform using OTel, Jaeger, and VictoriaMetrics to capture metrics, traces, and logs across microservices.}
        % \resumeItem{Designed and maintained CI/CD pipelines using Jenkins, GitLab CI, and Argo CD to drive automated build and deployment workflows from Git to on-premises and cloud-based Kubernetes clusters, leveraging Helm for standardized release management across services.}
        \resumeItem{Led end-to-end CI/CD toolchain upgrades — spanning the Jenkins controller and agents, Flux CD, Coverity, and Trivy — to remediate critical vulnerabilities, unlock new platform capabilities, and strengthen security posture and pipeline reliability.}
        \resumeItem{Refactored Jenkins shared libraries to consolidate duplicated pipeline logic into reusable components, improving maintainability and pipeline consistency across teams.}
        \resumeItem{Developed automation to continuously audit and auto-remediate GitLab repository settings across 150+ repositories, ensuring consistent configuration compliance and reducing manual governance overhead.}
        \resumeItem{Built a repository compliance audit system that identified stale repositories and enforced CI/CD gate compliance by triggering automated merge requests — prompting developers to resolve failing pipeline checks.}
        \resumeItem{Managed and upgraded cloud-based (AWS EKS) and on-premises (RKE2) Kubernetes clusters, ensuring platform reliability, security compliance, and minimal workload disruption.}
        \resumeItem{Maintained and upgraded in-cluster Kubernetes platform components to continuously remediate CVEs, introduce new capabilities, and uphold a hardened security posture.}
        \resumeItem{Orchestrated workload migrations to HPE data centers following company acquisition, ensuring service continuity and minimal downtime during infrastructure cutover.}
        \resumeItem{Evaluated and onboarded new DevOps tooling through structured POCs based on developer requirements, accelerating adoption of vetted solutions across engineering teams.}
        \resumeItem{Managed artifact lifecycle in JFrog Artifactory — including Docker base images and binary packages across technology stacks — onboarding developer-requested artifacts to remediate Trivy-detected vulnerabilities and maintain a secure, up-to-date catalog for microservice teams.}
        \resumeItem{Participated in an on-call rotation as the primary point of contact for DevOps platform and infrastructure support tickets, ensuring timely triage and resolution.}
      \resumeItemListEnd

    \resumeSubheading
      {Nokia}{Jul 2022 -- Aug 2025}
      {R\&D Engineer - DevOps}{Bengaluru, Karnataka}
      \resumeItemListStart
        \resumeItem{Managed CI/CD pipelines using Jenkins and Argo CD to automate build and deployment workflows from Git to on-premises and cloud-based Kubernetes clusters, leveraging Helm for standardized release management across services.}
        \resumeItem{Migrated from a self-hosted CI infrastructure to a centralized and secure CI platform, integrating SonarQube, JFrog Artifactory, and internal artifact repositories — improving security posture, reducing maintenance overhead, enhancing build reliability, and enabling centralized governance and compliance.}
        \resumeItem{Managed on-premises and cloud-based Kubernetes clusters, performing zero-downtime version upgrades and optimizing resource utilization through efficient bin packing.}
        \resumeItem{Led comprehensive software upgrades, applying security patches across all environments to mitigate vulnerabilities, enhance system resilience, and ensure compliance, in collaboration with security and operations teams.}
        \resumeItem{Configured and maintained AWS cloud infrastructure using Terraform, ensuring automated provisioning, scalability, and reliability.}
        \resumeItem{Developed and maintained automation scripts and internal tooling to streamline operational tasks and configuration management, reducing manual overhead and improving operational consistency.}
        \resumeItem{Diagnosed and resolved issues across CI/CD, development, QA, staging, and production environments, collaborating with development, testing, and operations teams.}
        \resumeItem{Maintained and enhanced observability stacks using Prometheus, Grafana, VictoriaMetrics, Loki, and ELK/OpenSearch — improving system health visibility and enabling efficient troubleshooting workflows.}
      \resumeItemListEnd

    \resumeSubheading
      {Test Yantra}{Apr 2021 -- Jun 2022}
      {DevOps Engineer}{Bengaluru, Karnataka}
      \resumeItemListStart
        \resumeItem{Designed and deployed scalable, high-availability AWS infrastructure using EC2, Auto Scaling Groups, S3, and EBS, integrating CloudWatch for monitoring and Route 53 for DNS management.}
        \resumeItem{Refactored existing Terraform modules to align with latest practices and provider versions, reducing tech debt and improving module reusability.}
        \resumeItem{Built and optimized Jenkins pipelines to automate end-to-end CI/CD for applications hosted on AWS, improving delivery velocity and stability.}
        \resumeItem{Managed application deployments in Kubernetes clusters across Dev, QA, Staging, Production, and DR environments using Helm to standardize and streamline release processes.}
        \resumeItem{Performed OS-level security patching on EC2 instances to remediate CVEs, maintaining system stability and ensuring compliance with security baselines.}
        \resumeItem{Provisioned and upgraded Kubernetes clusters based on team requirements, keeping the platform current with the latest versions and associated tooling.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
        {\textbf{Homelab}  \href{https://github.com/shreenivasa4/homelab}
        {\faGithub} $|$ \emph{Kubernetes, Flux CD, GitHub Actions, Terraform, Amazon Web Services}}{Dec 2025}
          \resumeItemListStart
            \resumeItem{A personal Kubernetes-based homelab built to self-host services, experiment with cloud-native tooling, and maintain a hands-on environment for continuous learning.}
            \resumeItem{Implemented GitOps workflows using Flux CD to continuously reconcile cluster state with a Git repository, enabling declarative and auditable infrastructure management.}
            \resumeItem{Provisioned and managed AWS infrastructure with Terraform, automating resource lifecycle for compute, networking, and storage components.}
            \resumeItem{Automated container image builds and deployments via GitHub Actions, integrating security scanning and pushing images to a private registry.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------CERTIFICATIONS-----------
\section{Certifications}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{{CKA: Certified Kubernetes Administrator}
     \href{https://www.credly.com/badges/1573fc1c-d95f-4142-ace0-d3209fc1a4aa}
     {\faExternalLinkSquare*}} \hfill \textbf{Issued Dec 2024 $\cdot$ Expires Dec 2026} \\
     \textbf{{CKAD: Certified Kubernetes Application Developer}
     \href{https://www.credly.com/badges/d18c3320-953b-4970-bdc0-bfcba9331298}
     {\faExternalLinkSquare*}} \hfill \textbf{Issued Jan 2025 $\cdot$ Expires Jan 2027} \\
     \textbf{{CKS: Certified Kubernetes Security Specialist}
     \href{https://www.credly.com/badges/4756ed79-afb6-45aa-a27a-c7395e08168c}
     {\faExternalLinkSquare*}} \hfill \textbf{Issued Mar 2025 $\cdot$ Expires Mar 2027} \\
    }}
\end{itemize}
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Visvesvaraya Technological University}{Aug 2016 -- Oct 2020}
      {Bachelor of Engineering in Computer Science and Engineering}{Ramanagara, Karnataka}
  \resumeSubHeadingListEnd

\end{document}